\mytitle

### 2016-12-02 report/evaluation.tex
Fix small typos

Comparing \epto and \jgroups in terms of bandwidth when we increase the number of events sent per second, we can see the bandwidth doubling in both cases. In lower peers scenario such as the ones presented in \autoref{fig:bandwidth} \jgroups has the upper hand. Since \epto has a worse baseline we will reach the maximum bandwidth possible much quicker when increasing the event throughput.

Comparing \epto and \jgroups in terms of bandwidth when we increase the number of peers, \epto is performing better than \jgroups. Where \jgroups basically has to double the bandwidth usage of the coordinator, \epto only increases it by 50\% or less. \jt{logarithmic I think as per the formula}. Thus in a scenario where we have many peers \epto will be more efficient than \jgroups at not reaching the maximum bandwidth.

@@

\subsection{Total Bytes sent/received}
\begin{figure}[h]
	\centering
	\input{figures/total-bytes.tex}
	\vspace{-2mm} 
	\caption{Total bytes sent/received during an average experiment}
	\vspace{-2mm} 
	\label{fig:total-bandwidth}
\end{figure}
In \autoref{fig:total-bandwidth}, \epto has a worse baseline than \jgroups. This is expected as \epto sends $c*n*\log_2 n$ messages per events and \jgroups sends at minimum $n$ messages per event so we should have at least $c*\log_2 n$ more messages sent in \epto if \jgroups is perfect. Here we are well within this ratio.

@@

The fact that killing the coordinator or not is of no effect on the total bandwidth used tends to show the hypothesis to be correct.
\subsection{Local Times}
\label{sub:local-times}
\jt{Having a table for each percentile figure might be a good idea to put numbers for key percentiles (min,50th,max) for example}
\begin{figure}[h]
	\centering
	\input{figures/local-times.tex}
	\vspace{-2mm} 
	\caption{Local dissemination times}
	\vspace{-2mm}
	\label{fig:local-times} 
\end{figure}

@@

\begin{figure}[h]
	\centering
	\input{figures/global-times-churn.tex}
	\vspace{-2mm} 
	\caption{Global dissemination times with churn}
	\vspace{-2mm} 
	\label{fig:global-times-churn} 
\end{figure}
We computed global times as well. They are represented in \autoref{fig:global-times} and \autoref{fig:global-times-churn}. These global times are of less interest than their local counterpart as they differences in clocks between hosts can skew this measurement.

@@

However when killing and adding nodes, we notice that \jgroups delivers more than 2000 less events than \epto, even when the coordinator is not killed.

>>>>

Comparing \epto and \jgroups in terms of bandwidth when we increase the number of events sent per second, we can see the bandwidth doubling in both cases.In lower peers scenario such as the ones presented in \autoref{fig:bandwidth} \jgroups is clearly at an advantage. Since \epto has a worse baseline we will reach the maximum bandwidth possible much quicker when increasing the event throughput.

Comparing \epto and \jgroups in terms of bandwidth when we increase the number of peers, \epto is performing better than \jgroups. Where \jgroups basically has to double the bandwidth usage of the coordinator, \epto only increases it by 50\% or less. \jt{logarithmic I think as was expected}. Thus in a scenario where we have many peers \epto will be more efficient than \jgroups at not reaching the maximum bandwidth.

@@

\subsection{Total Bytes sent/received}
\begin{figure}[h]
	\centering
	\input{figures/total-bytes.tex}
	\vspace{-2mm} 
	\caption{Total bytes sent/received during an average experiment}
	\vspace{-2mm} 
	\label{fig:total-bandwidth}
\end{figure}
In \autoref{fig:total-bandwidth}, \epto has a worse baseline than \jgroups. This is expected as \epto sends $c*n*\log_2 n$ messages per events and \jgroups sends at least $n$ messages per event so we should have at least $c*\log_2 n$ more messages sent in \epto if \jgroups is perfect. Here we are well within this ratio.

@@

The fact that killing the coordinator or not has no effect on the total bandwidth used tends to show the hypothesis to be correct.
\subsection{Local Times}
\label{sub:local-times}
\jt{Having a table for each percentile figure might be a good idea to put numbers for key percentiles (min,50th,max) for example}
\begin{figure}[h]
	\centering
	\input{figures/local-times.tex}
	\vspace{-2mm} 
	\caption{Local dissemination times}
	\vspace{-2mm}
	\label{fig:local-times} 
\end{figure}

@@

\begin{figure}[h]
	\centering
	\input{figures/global-times-churn.tex}
	\vspace{-2mm} 
	\caption{Global dissemination times with churn}
	\vspace{-2mm} 
	\label{fig:global-times-churn} 
\end{figure}
We computed global times as well. They are represented in \autoref{fig:global-times} and \autoref{fig:global-times-churn}. These global times are of less interest than their local counterpart as the differences in clocks between hosts can skew this measurement.

@@

However when killing and adding nodes \epto is clearly superior, delivering more than 2000 more events than \jgroups, even when \jgroups coordinator is not killed.
